### 2018-02-05 Graduate - Introduction to Analysis II/HW3/3HW20180204.tex
add prob 1, 2

\noindent In problems 3. - 5., references such as III.2.7 refer to Problem 7 in Section 2 of Chapter III in Conway's book.\smallskip

@@

@@

\emph{Homework 2 is due on ICON by Midnight, February  11.}

@@

@@

\item Problem IV.1.5

\textbf{Sol.} By Proposition 1.3, 
$$
\begin{aligned}
V(\gamma) &= \int_{0}^{1}|\gamma'(t)|dt = \int_0^1 |\frac{1-i}{t^2}e^{\frac{-1+i}{t}}|dt = \int_{0}^{1} |\frac{1-i}{t^2}e^{-\frac{1}{t}}(\cos\frac{1}{t}+i\sin\frac{1}{t})|dt \\
&= \int_0^1\frac{e^{-\frac{1}{t}}}{t^2}\sqrt{(\cos\frac{1}{t}+\sin\frac{1}{t})^2+(\sin\frac{1}{t}-\cos\frac{1}{t})^2}dt = \int_0^1\sqrt{2}\frac{e^{-\frac{1}{t}}}{t^2}dt \\
&= \left.\sqrt{2}e^{-\frac{1}{t}}\right\arrowvert_{0}^{1} = \sqrt{2}e^{-1}.
\end{aligned}
$$
Hence $\gamma$ is rectifiable. The trace looks like the graph below:
\begin{figure}[!htb] \centering
\includegraphics[width = 5cm]{prob1.jpg}
\end{figure}

\item Problem IV.1.9

\textbf{Sol.}
$$
\int_\gamma \frac{1}{z}dz = \int_{0}^{2\pi} e^{-int}ine^{int}dt = 2\pi in.
$$

\item Problem IV.1.12

\textbf{Sol.}
$$
I(r) = \int_{\gamma} \frac{e^{iz}}{z}dz = \int_{0}^{2\pi}\frac{e^{ire^{it}}}{re^{it}}ire^{it}dt = \int_{0}^{2\pi}ie^{ire^{it}}dt = \int_{0}^{2\pi}ie^{-r\sin t}(\cos(r\cos t)+i\sin(r\cos t))dt.
$$
Then 
$$
|I(r)| \le \int_{0}^{2\pi}|ie^{-r\sin t}(\cos(r\cos t)+i\sin(r\cos t))|dt = \int_0^{2\pi}e^{-r\sin t}dt = \int_{0}^{\pi}+\int_{\pi}^{2\pi}e^{-r\sin t}dt.
$$
Pick an arbitrary $\epsilon > 0$, the first term
$$
\int_{0}^{\pi}e^{-r\sin t}dt = \int_0^\epsilon + \int_\epsilon^{\pi-\epsilon} + \int_{\pi-\epsilon}^{\pi}e^{-r\sin t}dt \le 2\epsilon + (\pi-2\epsilon)e^{-r\sin\epsilon}.
$$
Then when $r \to \infty$,
$$
\int_{0}^{\pi}e^{-r\sin t}dt \le 2\epsilon.
$$
By the arbitrariness of $\epsilon$, $\int_{0}^{\pi}e^{-r\sin t}dt \to 0$ when $r\to \infty$. It is the same for the second term $\int_{\pi}^{2\pi} $. Hence $\lim\limits_{r\to\infty}I(r) = 0 $.

\item Problem IV.1.13

\textbf{Sol (a).} 
$$
\int_{\gamma}z^{-\frac{1}{2}}dz = \left.\int_{0}^{\pi}e^{-\frac{1}{2}it}ie^{it}dt = 2e^{\frac{1}{2}it}\right\arrowvert_{0}^{\pi} = 2i-2.
$$
\textbf{(b).}
$$
\int_{\gamma}z^{-\frac{1}{2}}dz = \left.\int_{2\pi}^{\pi}e^{-\frac{1}{2}it}ie^{it}dt = 2e^{\frac{1}{2}it}\right\arrowvert_{2\pi}^{\pi} = 2i+2.
$$

\item Problem IV.1.14

\textbf{Proof.} First, assume $\varphi$ is one-one. Then if $\varphi$ is not strictly increasing, suppose there exists $x < y \in [a, b]$, s.t. $\varphi(x) \ge \varphi(y)$. If $\varphi(x) = \varphi(y)$, it contradicts with that $\varphi$ is one-one. So $\varphi(x) > \varphi(y)$. Since $\varphi(x) > c$ (otherwise $\varphi(y) < c$ contradicts with $\varphi([a, b]) \ge c$), by continuity of $\varphi$, $\exists z \in [a, x]$, s.t. $\varphi(z) = \varphi(y)$, which makes a contradiction. Thus $\varphi$ is strictly increasing.

Now assume $\varphi$ is strictly increasing, then $\varphi$ is an injection. Besides, for each $y\in [c, d]$, by continuity of $\varphi$, there is a $x\in[a, b]$, s.t. $\varphi(x) = y$. Hence $\varphi$ is a bijection.

\item Problem IV.1.20

\textbf{Sol.} 
$$
\int_{\gamma}\frac{1}{z^2-1}dz = \int_{0}^{2\pi}\frac{1}{(e^{it}+1)^2-1}ie^{it}dt = \left.\int_{0}^{2\pi}\frac{i}{2+e^{it}}dt = \frac{1}{2}i(t+i\ln(2+e^{it}))\right\arrowvert_{0}^{2\pi} = \pi i
$$

\item Problem IV.2.1

\textbf{Proof.} We need to show that $g$ is continuous at each $t_0\in[c, d] $. In fact, $\forall \epsilon > 0$, since $\varphi$ is continuous, $\exists \delta > 0$, when $|t_1-t_0| < \delta $, we have $|\varphi(s, t_1)-\varphi(s, t_0)| < \frac{\epsilon}{b-a}$. Thus when $|t_1-t_0| < \delta $,
$$
|g(t_1)-g(t_0)| \le \int_{a}^{b}|\varphi(s, t_1)-\varphi(s, t_2)|ds < \int_{a}^{b}\frac{\epsilon}{b-a}ds = \epsilon.
$$
Hence $g$ is continuous at $t_0 $.

\item Problem IV.2.2  (Please note.  This problem will be used a number of places in the theory we will develop.)

\textbf{Proof.} 
First, by the same deduction of last problem, we can show $g$ is continuous. Thus, if we prove that $g$ is differentiable with $g'$ given by 
$$
g'(z) = \int_{\gamma}\frac{\partial\varphi}{\partial z}(w, z)dz,
$$
then $g'$ is continuous since $\frac{\partial \varphi}{\partial z}$ is continuous. Hence we only need to prove the formula for $g'$.

For a fixed point $z_0 $ in G, let $\epsilon > 0$. Denote $\frac{\partial \varphi}{\partial z}$ by $\phi$. Pick a closed set $F\subset G$ s.t. $z_0\in F $, then since $\gamma $ is rectifiable, $\phi$ is uniformly continuous on $\gamma\times F$. Thus, there is a $\delta > 0$ s.t. $|\phi(w', z')-\phi(w, z)| < \epsilon$ when $(w-w')^2+(z-z')^2<\delta^2 $. In particular, 
$$
|\phi(w, z)-\phi(w, z_0)| < \epsilon
$$
when $|z-z_0| < \delta$. Hence,
$$
|\int_{z_0}^{z}\phi(w, z)-\phi(w, z_0)dw| \le \epsilon|z-z_0|.
$$
For a fixed $w\in\gamma$, $\Phi(z) = \varphi(w, z)-z\phi(w, z_0)$ is a primitive of $\phi(w, z)-\phi(w, z_0)$. By Fundamental Thm of Calculus, 
$$
|\varphi(w, z)-\varphi(w, z_0)-(z-z_0)\phi(w, z_0)|\le \epsilon |z-z_0|
$$
for each $w$ when $|z-z_0|< \delta$. Hence
$$
|\frac{g(z)-g(z_0)}{z-z_0}-\int_{\gamma}\phi(w, z_0)dw|\le \epsilon\int_{\gamma}1ds.
$$
when $0 < |z-z_0| < \delta $. Hence by arbitrariness of $\epsilon$ we proved the proposition.

\item Problem IV.2.3

\textbf{Proof.} Let $\phi = \frac{\varphi(w)}{w-z}$, then $\frac{\partial \phi}{\partial z} = (w-z)^{-2}\varphi(w) $ is continuous on $\mathbb{C}-\{\gamma\}$. Thus by exercise 2 we know $g$ is analytic, and
$$
g'(z) = \int_{\gamma}\varphi(w)(w-z)^{-2}dw.
$$
Now suppose for $k \le n$,
$$
g^{(k)}(z) = n!\int_{\gamma}\varphi(w)(w-z)^{-(n+1)}dw,
$$
then
$$
g^{(n+1)}(z) = (n+1)n!\int_{\gamma}\varphi(w)(w-z)^{-(n+2)}dw = (n+1)!\int_{\gamma}\varphi(w)(w-z)^{-(n+2)}dw.
$$
By induction we know the result is correct.

>>>>

\noindent\textbf{Instructions}:References such as III.2.7 refer to Problem 7 in Section 2 of Chapter III in Conway's book.\smallskip

@@

\noindent \textbf{Reminder: Exam I will be from 6:30 to 10:30 on Thursday, February 15 in Room 40 of Schaeffer Hall.}

@@

\emph{Homework 3 is due in your Dropbox folder by 11:59, Sunday , February 19.}

@@

\noindent Working on this homework will help you with Exam I, so please don't put it off until after the exam.

@@

\item Problem IV.2.4

\textbf{(a)}
By Abel's transform, let $\{a_n\}, \{b_n\}$ be two sequences, and $B_k = \sum\limits_{i=1}^{k}b_i $. Then
$$
\sum_{k=1}^{n}a_kb_k = a_nB_n - \sum_{k=1}^{n-1}(a_{k+1}-a_k)B_k.
$$
Hence for each fixed $n$, denote $\sum\limits_{k=1}^{n}a_k $ by $A_n $
$$
C_n = \lim_{r\to1^-}\sum_{k=1}^{n}a_kr^k = r^nA_n - \sum_{k=1}^{n-1}r^k(r-1)A_k.
$$
Since $\sum a_n(z-a)^n $ have radius of convergence 1,
$$
\lim_{r\to 1^-} \sum_{n=1}^{\infty}a_nr^n < \infty,
$$
then we can change the order of limits:
$$
\lim_{r\to 1^-}\lim_{n\to\infty}\sum_{k=1}^{n}a_kr^k = \lim_{n\to\infty}\lim_{r\to 1^-}\sum_{k=1}^{n}a_kr^k = \lim_{n\to\infty} A_n
$$
since each $A_k $ is a finite number, which comes from $\sum a_n $ converges to $A$. Hence,
$$
\lim_{r\to 1^-}\sum_{n=1}^{\infty}a_nr^n = \lim_{n\to\infty} A_n = A.
$$

\textbf{(b)}
Consider $a_n = \frac{(-1)^{n+1}}{n} $, then by Proposition III.1.4,
$$
\lim_{n\to\infty}\left|\frac{a_n}{a_{n+1}}\right| = \lim\frac{n+1}{n} = 1.
$$
Hence the series $\sum a_n(z-a)^n $ have radius of convergence 1. Since the series $\sum a_n $ is a Leibniz series, then it converges to $A < \infty$.

Now consider the function $f(z) = \log z$, it is analytic on $|z-1| < 1$, and it has power series expansion
$$
f(z) = \sum_{n=0}^{\infty}b_n (z-1)^n,
$$
where $b_n = \frac{1}{n!}f^{(n)}(1) = \frac{(-1)^{n-1}}{n} (n \ge 1), $ and $b_0 = 0 $. By this we can find $a_i = b_i $ for each $i \ge 0$, thus
$$
\sum a_n = f(2) = \log 2
$$

\item Problem IV.2.6

\textbf{Sol.} In the region where $f(z) = \sqrt{z}$ is analytic, 
$$
f(z) = \sum_{n=0}^{\infty}a_n(z-1)^n,
$$
where
$$
a_n = \frac{1}{n!}f^{(n)}(1) = \frac{(-1)^{(n-1)}}{n!}\frac{(2n-3)!!}{2^{n}} (n \ge 1), ~a_0 = 1.
$$
and since
$$
\lim_{n\to\infty}\left|\frac{a_n}{a_{n+1}}\right| = \lim_{n\to\infty} \frac{2n+2}{2n-1} = 1,
$$
we know the radius of convergence is 1.

\item Problem IV.2.9

\item Problem IV.2.11

\item Problem IV.3.3

\item Problem IV.3.6

\item Problem IV.3.14

\item Problem IV.4. 2

\item Problem IV. 4.3

\item Problem IV.5.7

\item Problem IV.5.9
